Fast Construction of Inter-Object Spacing Representations

### 2017-04-03 paper.tex
updated figure 6

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:vascular-1}
    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/04-Pruned.PNG} }
  \subfloat[][]{
    \label{fig:vascular-2}
    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/06-Initial-Conflicts.PNG} }
  \subfloat[][]{
    \label{fig:vascular-3}
%    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/08-Resolved-Quadtree.PNG} }
    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/13-Resolved-Quadtree.PNG} }
  \caption{\red{Can you give some details on this dataset -- what it is etc}
    \protect\subref{fig:vascular-1} Initial vertex quadtree after pruning.
    \protect\subref{fig:vascular-2} All conflict cells of the initial quadtree.
    \protect\subref{fig:vascular-3} After conflict cell resolution. No quadtree cell intersects more than one object. \red{Can you get a similar figure to this that has closed polygons and is maybe zoomed in a little more two a few nice-looking polygons?}
  }
  \label{fig:vascular}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:vascular-1}
    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/04-Pruned.PNG} }
  \subfloat[][]{
    \label{fig:vascular-2}
    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/06-Initial-Conflicts.PNG} }
  \subfloat[][]{
    \label{fig:vascular-3}
%    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/08-Resolved-Quadtree.PNG} }
    \includegraphics[width=0.31\columnwidth]{Nathan/vascular-bundles/14-Resolved-Quadtree.PNG} }
  \caption{A large set of uniquely labeled polygons constructed from connected component analysis on a photograph of vascular cambium, a type of plant tissue.
    \protect\subref{fig:vascular-1} Initial vertex quadtree after pruning.
    \protect\subref{fig:vascular-2} All conflict cells of the initial quadtree.
    \protect\subref{fig:vascular-3} After conflict cell resolution. No quadtree cell intersects more than one object.
  }
  \label{fig:vascular}
\end{figure}
